Democracy, Public Support, and Measurement Uncertainty

### 2021-06-26 paper/dcpo_demsupport.Rmd

# Replications of Full Pack of Models in Claassen 2020a,b

```{r plot-fullpackAJPS, fig.cap= "The Effect of Public Support on Democracy", fig.width=7.5, fig.height=10, eval=TRUE}

# Very weird phenomenon that the same type of rds files needs different ways to read
# Suggesting using the qs or csv data type in future.
result_cls <- readRDS(here::here("output", "estimates_clsMeanAJPS.RDS"))
result_clsUncertain <- readRDS(here::here("output", "estimates_clsAJPS.RDS"))
result_dcpoUncertain <- readRDS(here::here("output", "estimates_dcpoAJPS.RDS"))

result_pooled <- bind_rows(
  mutate(result_cls$pooled[[1]], model = "Claassen 2020a"),
  mutate(result_clsUncertain$pooled[[1]], model = "Claassen w/ Uncertainty"),
  mutate(result_dcpoUncertain$pooled[[1]], model = "DCPO")
) %>% 
  mutate(type = "Pooled")

result_gmm <- bind_rows(
  mutate(result_cls$gmm[[1]], model = "Claassen 2020a"),
  mutate(result_clsUncertain$gmm[[1]], model = "Claassen w/ Uncertainty"),
  mutate(result_dcpoUncertain$gmm[[1]], model = "DCPO")
) %>% 
  mutate(type = "GMM")

result_pooledAJPS <- bind_rows(result_pooled, result_gmm) %>%
  filter(term != "(Intercept)") %>%
  mutate(
    term = rep(
      c("Democracy\n (t-1)",
        "Democracy\n (t-2)",
      "Support\n (t-1)",
      "Log GDP\n per capita\n (t-1)",
      "GDP per\n capita growth\n (t-1)",
      "Regional\n democracy\n (t-1)",
      "Percent\n Muslim\n (t-1)",
      "Resource\n dependence\n (t-1)"),
    time = 6), 
    type = factor(type, levels = c("Pooled", "GMM")),
    model = factor(model, levels = c("Claassen 2020a", "Claassen w/ Uncertainty", "DCPO")))

# ggplot produces reversed plot, and embarrassed to say, I can't fix, again. Any thought?
# What I've tried
# 1. using guide_legend(reverse = TRUE) will change the legend's order not the plot.
# 2. ordering models with factor levels using the original names or even c("1", "2", "3")
# 2. redefining the order of model in the dataframe or in dwplot 
# 3. checking the dwplot codes, model works in line 453, but nothing looks helpful
# 4. Every post online is to reverse

# the attemp to change the order of legends failed. Both factorize the model ahead or using the  guides(fill = guide_legend(reverse=TRUE)) fails
# The trick is  to use guide = guide_legend(reverse = TRUE) within scale_color_*(); see below in plotAJPS2. --FS

result_regime <- bind_rows(
  mutate(result_cls$`pooled-regime`[[1]], model = "Claassen 2020a"),
  mutate(result_clsUncertain$`pooled-regime`[[1]], model = "Claassen w/ Uncertainty"),
  mutate(result_dcpoUncertain$`pooled-regime`[[1]], model = "DCPO")
) %>% 
  mutate(type = "Pooled")

result_regimeGmm <- bind_rows(
  mutate(result_cls$`gmm-regime`[[1]], model = "Claassen 2020a"),
  mutate(result_clsUncertain$`gmm-regime`[[1]], model = "Claassen w/ Uncertainty"),
  mutate(result_dcpoUncertain$`gmm-regime`[[1]], model = "DCPO")
) %>% 
  mutate(type = "GMM")

result_regimeAJPS <- bind_rows(result_regime, result_regimeGmm) %>%
  filter(term != "(Intercept)") %>%
  mutate(
    term = rep(
      c("Democracy\n (t-1)",
        "Democracy\n (t-2)",
      "Support\n demo only\n (t-1)",
      "Support\n auto only\n (t-1)",
      "Log GDP\n per capita\n (t-1)",
      "GDP per\n capita growth\n (t-1)",
      "Regional\n democracy\n (t-1)",
      "Percent\n Muslim\n (t-1)",
      "Resource\n dependence\n (t-1)"),
    time = 6), 
    type = factor(type, levels = c("Pooled", "GMM")),
    model = factor(model, levels = c("Claassen 2020a", "Claassen w/ Uncertainty", "DCPO")))

terms2 <- factor(rev(c("Democracy[t-1]",
                       "Democracy[t-2]",
                       "Support[t-1] (democracies~only)",
                       "Support[t-1] (autocracies~only)",
                       "Log~GDP~per~capita[t-1]",
                       "GDP~per~capita~growth[t-1]",
                       "Regional~democracy[t-1]",
                       "Percent~Muslim[t-1]",
                       "Resource~dependence[t-1]")), levels =
                   rev(c("Democracy[t-1]",
                         "Democracy[t-2]",
                         "Support[t-1] (democracies~only)",
                         "Support[t-1] (autocracies~only)",
                         "Log~GDP~per~capita[t-1]",
                         "GDP~per~capita~growth[t-1]",
                         "Regional~democracy[t-1]",
                         "Percent~Muslim[t-1]",
                         "Resource~dependence[t-1]")))

plot_AJPS2 <- dwplot(result_regimeAJPS, dodge_size = 0.8, by_2sd = FALSE) +
    scale_y_discrete(labels = parse(text = levels(terms2))) +
  scale_color_grey(start = 0.4, end = 0.8, guide = guide_legend(reverse = TRUE)) +
  labs(
    title = "",
    subtitle = "Regime Specific"
  ) +
  facet_wrap(~type, scales = "free_x") +
  theme(legend.position = "bottom", 
        legend.title = element_blank())

legend <- get_legend(plot_AJPS2)

plot_AJPS2 <- plot_AJPS2 + theme(legend.position = "none")

grid.arrange(plot_AJPS1, plot_AJPS2, legend, ncol = 1)

```{r plot-fullpackAJPSfull, fig.cap= "The Effect of Public Support on Democracy", eval = TRUE, fig.width=7.5, fig.height=7, eval=TRUE}

# Very weird phenomenon that the same type of rds files needs different ways to read
# Suggesting using the qs or csv data type in future.
result_cls <- readRDS(here("output", "estimates_clsMeanAJPS.RDS"))
result_clsUncertainFull <- readRDS(here("output", "estimates_clsAJPSfullUncertain.RDS"))
result_dcpoUncertainFull <- readRDS(here("output", "estimates_dcpoAJPSfullUncertain.RDS"))

result_pooled <- bind_rows(
  mutate(result_cls$pooled[[1]], model = "Claassen 2020a"),
  mutate(result_clsUncertainFull$pooled[[1]], model = "Claassen w/ Uncertainty"),
  mutate(result_dcpoUncertainFull$pooled[[1]], model = "DCPO")
) %>% 
  mutate(type = "Pooled")

result_gmm <- bind_rows(
  mutate(result_cls$gmm[[1]], model = "Claassen 2020a"),
  mutate(result_clsUncertainFull$gmm[[1]], model = "Claassen w/ Uncertainty"),
  mutate(result_dcpoUncertainFull$gmm[[1]], model = "DCPO")
) %>% 
  mutate(type = "GMM")

result_pooledAJPS <- bind_rows(result_pooled, result_gmm) %>%
  filter(term != "(Intercept)") %>%
  mutate(
    term = rep(
      c("Democracy\n (t-1)",
        "Democracy\n (t-2)",
      "Support\n (t-1)",
      "Log GDP\n per capita\n (t-1)",
      "GDP per\n capita growth\n (t-1)",
      "Regional\n democracy\n (t-1)",
      "Percent\n Muslim\n (t-1)",
      "Resource\n dependence\n (t-1)"),
    time = 6), 
    type = factor(type, levels = c("Pooled", "GMM")),
    model = factor(model, levels = c("Claassen 2020a", "Claassen w/ Uncertainty", "DCPO")))

# ggplot produces reversed plot, and embarrassed to say, I can't fix, again. Any thought?
# What I've tried
# 1. using guide_legend(reverse = TRUE) will change the legend's order not the plot.
# 2. ordering models with factor levels using the original names or even c("1", "2", "3")
# 2. redefining the order of model in the dataframe or in dwplot 
# 3. checking the dwplot codes, model works in line 453, but nothing looks helpful
# 4. Every post online is to reverse

# the attemp to change the order of legends failed. Both factorize the model ahead or using the  guides(fill = guide_legend(reverse=TRUE)) fails
# The trick is  to use guide = guide_legend(reverse = TRUE) within scale_color_*(); see below in plotAJPS2. --FS

result_regime <- bind_rows(
  mutate(result_cls$`pooled-regime`[[1]], model = "Claassen 2020a"),
  mutate(result_clsUncertainFull$`pooled-regime`[[1]], model = "Claassen w/ Uncertainty"),
  mutate(result_dcpoUncertainFull$`pooled-regime`[[1]], model = "DCPO")
) %>% 
  mutate(type = "Pooled")

result_regimeGmm <- bind_rows(
  mutate(result_cls$`gmm-regime`[[1]], model = "Claassen 2020a"),
  mutate(result_clsUncertainFull$`gmm-regime`[[1]], model = "Claassen w/ Uncertainty"),
  mutate(result_dcpoUncertainFull$`gmm-regime`[[1]], model = "DCPO")
) %>% 
  mutate(type = "GMM")

result_regimeAJPS <- bind_rows(result_regime, result_regimeGmm) %>%
  filter(term != "(Intercept)") %>%
  mutate(
    term = rep(
      c("Democracy\n (t-1)",
        "Democracy\n (t-2)",
      "Support\n demo only\n (t-1)",
      "Support\n auto only\n (t-1)",
      "Log GDP\n per capita\n (t-1)",
      "GDP per\n capita growth\n (t-1)",
      "Regional\n democracy\n (t-1)",
      "Percent\n Muslim\n (t-1)",
      "Resource\n dependence\n (t-1)"),
    time = 6), 
    type = factor(type, levels = c("Pooled", "GMM")),
    model = factor(model, levels = c("Claassen 2020a", "Claassen w/ Uncertainty", "DCPO")))

terms2 <- factor(rev(c("Democracy[t-1]",
                       "Democracy[t-2]",
                       "Support[t-1] (democracies~only)",
                       "Support[t-1] (autocracies~only)",
                       "Log~GDP~per~capita[t-1]",
                       "GDP~per~capita~growth[t-1]",
                       "Regional~democracy[t-1]",
                       "Percent~Muslim[t-1]",
                       "Resource~dependence[t-1]")), levels =
                   rev(c("Democracy[t-1]",
                         "Democracy[t-2]",
                         "Support[t-1] (democracies~only)",
                         "Support[t-1] (autocracies~only)",
                         "Log~GDP~per~capita[t-1]",
                         "GDP~per~capita~growth[t-1]",
                         "Regional~democracy[t-1]",
                         "Percent~Muslim[t-1]",
                         "Resource~dependence[t-1]")))

plot_AJPS2 <- dwplot(result_regimeAJPS, dodge_size = 0.8, by_2sd = FALSE) +
    scale_y_discrete(labels = parse(text = levels(terms2))) +
  scale_color_grey(start = 0.4, end = 0.8, guide = guide_legend(reverse = TRUE)) +
  labs(
    title = "",
    subtitle = "Regime Specific"
  ) +
  facet_wrap(~type, scales = "free_x") +
  theme(legend.position = "bottom", 
        legend.title = element_blank())

legend <- get_legend(plot_AJPS2)

plot_AJPS2 <- plot_AJPS2 + theme(legend.position = "none")

grid.arrange(plot_AJPS1, plot_AJPS2, legend, ncol = 1)

```{r plot-fullpackAPSR, fig.cap= "The Effect of Democratic Mood on Institutional Democratization based on DCPO", fig.width=7.5, fig.height=10, eval=TRUE}

result_clsAPSR <- readRDS(here("output", "estimates_clsMeanAPSR.RDS"))
result_clsUncertainAPSR <- readRDS(here("output", "estimates_clsAPSR.RDS"))
result_dcpoUncertainAPSR <- readRDS(here("output", "estimates_dcpoAPSR.RDS"))

# Regime compacted ####

result_ecm1 <- bind_rows(
  mutate(result_clsAPSR$pooled1[[1]], model = "Claassen 2020a"),
  mutate(result_clsUncertainAPSR$pooled1[[1]], model = "Claassen w/ Uncertainty"),
  mutate(result_dcpoUncertainAPSR$pooled1[[1]], model = "DCPO")
) %>% 
  mutate(type = "ECM")

result_fd1 <- bind_rows(
  mutate(result_clsAPSR$fd1[[1]], model = "Claassen 2020a"),
  mutate(result_clsUncertainAPSR$fd1[[1]], model = "Claassen w/ Uncertainty"),
  mutate(result_dcpoUncertainAPSR$fd1[[1]], model = "DCPO")
) %>% 
  mutate(type = "First Difference")

result_APSR1 <- bind_rows(result_ecm1, result_fd1) %>%
  filter(term != "(Intercept)") %>%
  mutate(
    term = c(rep(
      c("Democratic Mood\n (t-1)",
        "Democratic Mood\n (t-2)",
      "Liberal Democracy\n (Difference)",
      "Liberal Democracy\n (t-1)",
      "Log GDP\n per capita\n (Difference)",
      "Log GDP\n (t-1)"),
    time = 3),
    rep(
      c("Liberal Democracy\n (Difference)", 
        "Log GDP\n per capita\n (Difference)"), 
      time = 3
    )),
    type = factor(type, levels = c("ECM", "First Difference")),
    model = factor(model, levels = c("Claassen 2020a", "Claassen w/ Uncertainty", "DCPO"))
  )

terms1 <- factor(rev(c("Support[t-1]",
                      "Support[t-2]",
                      "Delta~Liberal~democracy",
                      "Liberal~democracy[t-1]",
                      "Delta~Log~GDP~per~capita",
                      "Log~GDP[t-1]")),
                levels = rev(c("Support[t-1]",
                               "Support[t-2]",
                               "Delta~Liberal~democracy",
                               "Liberal~democracy[t-1]",
                               "Delta~Log~GDP~per~capita",
                               "Log~GDP[t-1]")))

plot_APSR1 <- dwplot(result_APSR1, dodge_size = 0.8, by_2sd = FALSE) +
  scale_y_discrete(labels = parse(text = levels(terms1))) +
  scale_color_grey(start = 0.4, end = 0.8, guide = guide_legend(reverse = TRUE)) +
  # scale_color_uiowa(name = "", palette = "digitMixed") +
  labs(
    title = "DV: Public Support for Democracy",
    subtitle = "Regime Compacted"
  ) +
  facet_wrap(~type, scales = "free_x") + 
  theme(legend.position = "none")

result_ecm2 <- bind_rows(
  mutate(result_clsAPSR$pooled2[[1]], model = "Claassen 2020a"),
  mutate(result_clsUncertainAPSR$pooled2[[1]], model = "Claassen w/ Uncertainty"),
  mutate(result_dcpoUncertainAPSR$pooled2[[1]], model = "DCPO")
) %>% 
  mutate(type = "ECM")

result_fd2 <- bind_rows(
  mutate(result_clsAPSR$fd2[[1]], model = "Claassen 2020a"),
  mutate(result_clsUncertainAPSR$fd2[[1]], model = "Claassen w/ Uncertainty"),
  mutate(result_dcpoUncertainAPSR$fd2[[1]], model = "DCPO")
) %>% 
  mutate(type = "First Difference")

result_APSR2 <- bind_rows(result_ecm2, result_fd2) %>%
  filter(term != "(Intercept)") %>%
  mutate(
    term = c(rep(
      c("Democratic Mood\n (t-1)",
        "Democratic Mood\n (t-2)",
      "Liberal Democracy\n (Difference)",
      "Liberal Democracy\n (t-1)",
      "Log GDP\n per capita\n (Difference)",
      "Log GDP\n (t-1)",
      "Corruption\n (Difference)",
      "Corruption\n (t-1)"
      ),
    time = 3),
    rep(
      c("Liberal Democracy\n (Difference)", 
        "Log GDP\n per capita\n (Difference)",
        "Corruption\n (Difference)"), 
      time = 3
    )),
    type = factor(type, levels = c("ECM", "First Difference")),
    model = factor(model, levels = c("Claassen 2020a", "Claassen w/ Uncertainty", "DCPO"))
  )

terms2 <- factor(rev(c("Support[t-1]",
                      "Support[t-2]",
                      "Delta~Liberal~democracy",
                      "Liberal~democracy[t-1]",
                      "Delta~Log~GDP~per~capita",
                      "Log~GDP[t-1]",
                      "Delta~Corruption",
                      "Corruption[t-1]")),
                levels = rev(c("Support[t-1]",
                               "Support[t-2]",
                               "Delta~Liberal~democracy",
                               "Liberal~democracy[t-1]",
                               "Delta~Log~GDP~per~capita",
                               "Log~GDP[t-1]",
                               "Delta~Corruption",
                               "Corruption[t-1]")))

plot_APSR2 <- dwplot(result_APSR2, dodge_size = 0.8, by_2sd = FALSE) +
  scale_y_discrete(labels = parse(text = levels(terms2))) +
  scale_color_grey(start = 0.4, end = 0.8, guide = guide_legend(reverse = TRUE)) +
  # scale_color_uiowa(name = "", palette = "digitMixed") +
  labs(
    title = "",
    subtitle = "W. Corruption"
  ) +
  facet_wrap(~type, scales = "free_x") +
  theme(legend.position = "none")

# Regime specified ####

result_ecmReg1 <- bind_rows(
  mutate(result_clsAPSR$`pooled-regime1`[[1]], model = "Claassen 2020a"),
  mutate(result_clsUncertainAPSR$`pooled-regime1`[[1]], model = "Claassen w/ Uncertainty"),
  mutate(result_dcpoUncertainAPSR$`pooled-regime1`[[1]], model = "DCPO")
) %>% 
  mutate(type = "ECM")

result_fdReg1 <- bind_rows(
  mutate(result_clsAPSR$`fd-regime1`[[1]], model = "Claassen 2020a"),
  mutate(result_clsUncertainAPSR$`fd-regime1`[[1]], model = "Claassen w/ Uncertainty"),
  mutate(result_dcpoUncertainAPSR$`fd-regime1`[[1]], model = "DCPO")
) %>% 
  mutate(type = "First Difference")

result_RegAPSR1 <- bind_rows(result_ecmReg1, result_fdReg1) %>%
  filter(term != "(Intercept)") %>%
  mutate(
    term = c(rep(
      c("Democratic Mood\n (t-1)",
        "Democratic Mood\n (t-2)",
      "Electoral Democracy\n (Difference)",
      "Electoral Democracy\n (t-1)",
      "Minoritarian Democracy\n (Difference)",
      "Minoritarian Democracy\n (t-1)",
      "Log GDP\n per capita\n (Difference)",
      "Log GDP\n (t-1)"),
    time = 3),
    rep(
      c("Electoral Democracy\n (Difference)", 
        "Minoritarian Democracy\n (Difference)",
        "Log GDP\n per capita\n (Difference)"), 
      time = 3
    )),
    type = factor(type, levels = c("ECM", "First Difference")),
    model = factor(model, levels = c("Claassen 2020a", "Claassen w/ Uncertainty", "DCPO"))
  )

terms3 <- factor(rev(c("Support[t-1]",
                      "Support[t-2]",
                      "Delta~Electoral~democracy",
                      "Electoral~democracy[t-1]",
                      "Delta~Minoritarian~democracy",
                      "Minoritarian~democracy[t-1]",
                      "Delta~Log~GDP~per~capita",
                      "Log~GDP[t-1]")),
                levels = rev(c("Support[t-1]",
                      "Support[t-2]",
                      "Delta~Electoral~democracy",
                      "Electoral~democracy[t-1]",
                      "Delta~Minoritarian~democracy",
                      "Minoritarian~democracy[t-1]",
                      "Delta~Log~GDP~per~capita",
                      "Log~GDP[t-1]")))

plot_RegAPSR1 <- dwplot(result_RegAPSR1, dodge_size = 0.8, by_2sd = FALSE) +
  scale_y_discrete(labels = parse(text = levels(terms3))) +
  scale_color_grey(start = 0.4, end = 0.8, guide = guide_legend(reverse = TRUE)) +
  # scale_color_uiowa(name = "", palette = "digitMixed") +
  labs(
    title = "",
    subtitle = "Regime Specified"
  ) +
  facet_wrap(~type, scales = "free_x") + 
  theme(legend.position = "none")

result_ecmReg2 <- bind_rows(
  mutate(result_clsAPSR$`pooled-regime2`[[1]], model = "Claassen 2020a"),
  mutate(result_clsUncertainAPSR$`pooled-regime2`[[1]], model = "Claassen w/ Uncertainty"),
  mutate(result_dcpoUncertainAPSR$`pooled-regime2`[[1]], model = "DCPO")
) %>% 
  mutate(type = "ECM")

result_fdReg2 <- bind_rows(
  mutate(result_clsAPSR$`fd-regime2`[[1]], model = "Claassen 2020a"),
  mutate(result_clsUncertainAPSR$`fd-regime2`[[1]], model = "Claassen w/ Uncertainty"),
  mutate(result_dcpoUncertainAPSR$`fd-regime2`[[1]], model = "DCPO")
) %>% 
  mutate(type = "First Difference")

result_RegAPSR2 <- bind_rows(result_ecmReg2, result_fdReg2) %>%
  filter(term != "(Intercept)") %>%
  mutate(
    term = c(rep(
      c("Democratic Mood\n (t-1)",
        "Democratic Mood\n (t-2)",
      "Electoral Democracy\n (Difference)",
      "Electoral Democracy\n (t-1)",
      "Minoritarian Democracy\n (Difference)",
      "Minoritarian Democracy\n (t-1)",
      "Log GDP\n per capita\n (Difference)",
      "Log GDP\n (t-1)",
      "Corruption\n (Difference)",
      "Corruption\n (t-1)"
      ),
    time = 3),
    rep(
      c("Electoral Democracy\n (Difference)", 
        "Minoritarian Democracy\n (Difference)",
        "Log GDP\n per capita\n (Difference)",
        "Corruption\n (Difference)"), 
      time = 3
    )),
    type = factor(type, levels = c("ECM", "First Difference")),
    model = factor(model, levels = c("Claassen 2020a", "Claassen w/ Uncertainty", "DCPO"))
  )

terms4 <- factor(rev(c("Support[t-1]",
                      "Support[t-2]",
                      "Delta~Electoral~democracy",
                      "Electoral~democracy[t-1]",
                      "Delta~Minoritarian~democracy",
                      "Minoritarian~democracy[t-1]",
                      "Delta~Log~GDP",
                      "Log~GDP[t-1]",
                      "Delta~Corruption",
                      "Corruption[t-1]")),
                levels = rev(c("Support[t-1]",
                               "Support[t-2]",
                               "Delta~Electoral~democracy",
                               "Electoral~democracy[t-1]",
                               "Delta~Minoritarian~democracy",
                               "Minoritarian~democracy[t-1]",
                               "Delta~Log~GDP",
                               "Log~GDP[t-1]",
                               "Delta~Corruption",
                               "Corruption[t-1]")))

plot_RegAPSR2 <- dwplot(result_RegAPSR2, dodge_size = 0.8, by_2sd = FALSE) +
  scale_y_discrete(labels = parse(text = levels(terms4))) +
  scale_color_grey(start = 0.4, end = 0.8, guide = guide_legend(reverse = TRUE)) +
  # scale_color_uiowa(name = "", palette = "digitMixed") +
  labs(
    title = "",
    subtitle = "Regime Specified w. Corruption"
  ) +
  facet_wrap(~type, scales = "free_x") +
  theme(legend.position = "bottom", 
        legend.title = element_blank())

grid.arrange(plot_APSR1, plot_APSR2, plot_RegAPSR1, plot_RegAPSR2, legend, ncol = 1)
```

```{r plot-fullpackAPSRfull, fig.cap= "The Effect of Democracy on Public Support", eval = TRUE, fig.width=7, fig.height=10, eval=TRUE}

result_clsAPSR <- readRDS(here("output", "estimates_clsMeanAPSR.RDS"))
result_clsFullUncertainAPSR <- readRDS(here("output", "estimates_clsFullUncertainAPSR.RDS"))
result_dcpoFullUncertainAPSR <- readRDS(here("output", "estimates_dcpoUncertainAPSR.RDS"))

# Regime compacted ####

result_ecm1 <- bind_rows(
  mutate(result_clsAPSR$pooled1[[1]], model = "Claassen 2020a"),
  mutate(result_clsFullUncertainAPSR$pooled1[[1]], model = "Claassen w/ Uncertainty"),
  mutate(result_dcpoFullUncertainAPSR$pooled1[[1]], model = "DCPO")
) %>% 
  mutate(type = "ECM")

result_fd1 <- bind_rows(
  mutate(result_clsAPSR$fd1[[1]], model = "Claassen 2020a"),
  mutate(result_clsFullUncertainAPSR$fd1[[1]], model = "Claassen w/ Uncertainty"),
  mutate(result_dcpoFullUncertainAPSR$fd1[[1]], model = "DCPO")
) %>% 
  mutate(type = "First Difference")

result_APSR1 <- bind_rows(result_ecm1, result_fd1) %>%
  filter(term != "(Intercept)") %>%
  mutate(
    term = c(rep(
      c("Democratic Mood\n (t-1)",
        "Democratic Mood\n (t-2)",
      "Liberal Democracy\n (Difference)",
      "Liberal Democracy\n (t-1)",
      "Log GDP\n per capita\n (Difference)",
      "Log GDP\n (t-1)"),
    time = 3),
    rep(
      c("Liberal Democracy\n (Difference)", 
        "Log GDP\n per capita\n (Difference)"), 
      time = 3
    )),
    type = factor(type, levels = c("ECM", "First Difference")),
    model = factor(model, levels = c("Claassen 2020a", "Claassen w/ Uncertainty", "DCPO"))
  )

terms1 <- factor(rev(c("Support[t-1]",
                      "Support[t-2]",
                      "Delta~Liberal~democracy",
                      "Liberal~democracy[t-1]",
                      "Delta~Log~GDP~per~capita",
                      "Log~GDP[t-1]")),
                levels = rev(c("Support[t-1]",
                               "Support[t-2]",
                               "Delta~Liberal~democracy",
                               "Liberal~democracy[t-1]",
                               "Delta~Log~GDP~per~capita",
                               "Log~GDP[t-1]")))

plot_APSR1 <- dwplot(result_APSR1, dodge_size = 0.8, by_2sd = FALSE) +
  scale_y_discrete(labels = parse(text = levels(terms1))) +
  scale_color_grey(start = 0.4, end = 0.8, guide = guide_legend(reverse = TRUE)) +
  # scale_color_uiowa(name = "", palette = "digitMixed") +
  labs(
    title = "DV: Public Support for Democracy",
    subtitle = "Regime Compacted"
  ) +
  facet_wrap(~type, scales = "free_x") + 
  theme(legend.position = "none")

result_ecm2 <- bind_rows(
  mutate(result_clsAPSR$pooled2[[1]], model = "Claassen 2020a"),
  mutate(result_clsFullUncertainAPSR$pooled2[[1]], model = "Claassen w/ Uncertainty"),
  mutate(result_dcpoFullUncertainAPSR$pooled2[[1]], model = "DCPO")
) %>% 
  mutate(type = "ECM")

result_fd2 <- bind_rows(
  mutate(result_clsAPSR$fd2[[1]], model = "Claassen 2020a"),
  mutate(result_clsFullUncertainAPSR$fd2[[1]], model = "Claassen w/ Uncertainty"),
  mutate(result_dcpoFullUncertainAPSR$fd2[[1]], model = "DCPO")
) %>% 
  mutate(type = "First Difference")

result_APSR2 <- bind_rows(result_ecm2, result_fd2) %>%
  filter(term != "(Intercept)") %>%
  mutate(
    term = c(rep(
      c("Democratic Mood\n (t-1)",
        "Democratic Mood\n (t-2)",
      "Liberal Democracy\n (Difference)",
      "Liberal Democracy\n (t-1)",
      "Log GDP\n per capita\n (Difference)",
      "Log GDP\n (t-1)",
      "Corruption\n (Difference)",
      "Corruption\n (t-1)"
      ),
    time = 3),
    rep(
      c("Liberal Democracy\n (Difference)", 
        "Log GDP\n per capita\n (Difference)",
        "Corruption\n (Difference)"), 
      time = 3
    )),
    type = factor(type, levels = c("ECM", "First Difference")),
    model = factor(model, levels = c("Claassen 2020a", "Claassen w/ Uncertainty", "DCPO"))
  )

terms2 <- factor(rev(c("Support[t-1]",
                      "Support[t-2]",
                      "Delta~Liberal~democracy",
                      "Liberal~democracy[t-1]",
                      "Delta~Log~GDP~per~capita",
                      "Log~GDP[t-1]",
                      "Delta~Corruption",
                      "Corruption[t-1]")),
                levels = rev(c("Support[t-1]",
                               "Support[t-2]",
                               "Delta~Liberal~democracy",
                               "Liberal~democracy[t-1]",
                               "Delta~Log~GDP~per~capita",
                               "Log~GDP[t-1]",
                               "Delta~Corruption",
                               "Corruption[t-1]")))

plot_APSR2 <- dwplot(result_APSR2, dodge_size = 0.8, by_2sd = FALSE) +
  scale_y_discrete(labels = parse(text = levels(terms2))) +
  scale_color_grey(start = 0.4, end = 0.8, guide = guide_legend(reverse = TRUE)) +
  # scale_color_uiowa(name = "", palette = "digitMixed") +
  labs(
    title = "",
    subtitle = "W. Corruption"
  ) +
  facet_wrap(~type, scales = "free_x") +
  theme(legend.position = "none")

# Regime specified ####

result_ecmReg1 <- bind_rows(
  mutate(result_clsAPSR$`pooled-regime1`[[1]], model = "Claassen 2020a"),
  mutate(result_clsFullUncertainAPSR$`pooled-regime1`[[1]], model = "Claassen w/ Uncertainty"),
  mutate(result_dcpoFullUncertainAPSR$`pooled-regime1`[[1]], model = "DCPO")
) %>% 
  mutate(type = "ECM")

result_fdReg1 <- bind_rows(
  mutate(result_clsAPSR$`fd-regime1`[[1]], model = "Claassen 2020a"),
  mutate(result_clsFullUncertainAPSR$`fd-regime1`[[1]], model = "Claassen w/ Uncertainty"),
  mutate(result_dcpoFullUncertainAPSR$`fd-regime1`[[1]], model = "DCPO")
) %>% 
  mutate(type = "First Difference")

result_RegAPSR1 <- bind_rows(result_ecmReg1, result_fdReg1) %>%
  filter(term != "(Intercept)") %>%
  mutate(
    term = c(rep(
      c("Democratic Mood\n (t-1)",
        "Democratic Mood\n (t-2)",
      "Electoral Democracy\n (Difference)",
      "Electoral Democracy\n (t-1)",
      "Minoritarian Democracy\n (Difference)",
      "Minoritarian Democracy\n (t-1)",
      "Log GDP\n per capita\n (Difference)",
      "Log GDP\n (t-1)"),
    time = 3),
    rep(
      c("Electoral Democracy\n (Difference)", 
        "Minoritarian Democracy\n (Difference)",
        "Log GDP\n per capita\n (Difference)"), 
      time = 3
    )),
    type = factor(type, levels = c("ECM", "First Difference")),
    model = factor(model, levels = c("Claassen 2020a", "Claassen w/ Uncertainty", "DCPO"))
  )

terms3 <- factor(rev(c("Support[t-1]",
                      "Support[t-2]",
                      "Delta~Electoral~democracy",
                      "Electoral~democracy[t-1]",
                      "Delta~Minoritarian~democracy",
                      "Minoritarian~democracy[t-1]",
                      "Delta~Log~GDP~per~capita",
                      "Log~GDP[t-1]")),
                levels = rev(c("Support[t-1]",
                      "Support[t-2]",
                      "Delta~Electoral~democracy",
                      "Electoral~democracy[t-1]",
                      "Delta~Minoritarian~democracy",
                      "Minoritarian~democracy[t-1]",
                      "Delta~Log~GDP~per~capita",
                      "Log~GDP[t-1]")))

plot_RegAPSR1 <- dwplot(result_RegAPSR1, dodge_size = 0.8, by_2sd = FALSE) +
  scale_y_discrete(labels = parse(text = levels(terms3))) +
  scale_color_grey(start = 0.4, end = 0.8, guide = guide_legend(reverse = TRUE)) +
  # scale_color_uiowa(name = "", palette = "digitMixed") +
  labs(
    title = "",
    subtitle = "Regime Specified"
  ) +
  facet_wrap(~type, scales = "free_x") + 
  theme(legend.position = "none")

result_ecmReg2 <- bind_rows(
  mutate(result_clsAPSR$`pooled-regime2`[[1]], model = "Claassen 2020a"),
  mutate(result_clsFullUncertainAPSR$`pooled-regime2`[[1]], model = "Claassen w/ Uncertainty"),
  mutate(result_dcpoFullUncertainAPSR$`pooled-regime2`[[1]], model = "DCPO")
) %>% 
  mutate(type = "ECM")

result_fdReg2 <- bind_rows(
  mutate(result_clsAPSR$`fd-regime2`[[1]], model = "Claassen 2020a"),
  mutate(result_clsFullUncertainAPSR$`fd-regime2`[[1]], model = "Claassen w/ Uncertainty"),
  mutate(result_dcpoFullUncertainAPSR$`fd-regime2`[[1]], model = "DCPO")
) %>% 
  mutate(type = "First Difference")

result_RegAPSR2 <- bind_rows(result_ecmReg2, result_fdReg2) %>%
  filter(term != "(Intercept)") %>%
  mutate(
    term = c(rep(
      c("Democratic Mood\n (t-1)",
        "Democratic Mood\n (t-2)",
      "Electoral Democracy\n (Difference)",
      "Electoral Democracy\n (t-1)",
      "Minoritarian Democracy\n (Difference)",
      "Minoritarian Democracy\n (t-1)",
      "Log GDP\n per capita\n (Difference)",
      "Log GDP\n (t-1)",
      "Corruption\n (Difference)",
      "Corruption\n (t-1)"
      ),
    time = 3),
    rep(
      c("Electoral Democracy\n (Difference)", 
        "Minoritarian Democracy\n (Difference)",
        "Log GDP\n per capita\n (Difference)",
        "Corruption\n (Difference)"), 
      time = 3
    )),
    type = factor(type, levels = c("ECM", "First Difference")),
    model = factor(model, levels = c("Claassen 2020a", "Claassen w/ Uncertainty", "DCPO"))
  )

terms4 <- factor(rev(c("Support[t-1]",
                      "Support[t-2]",
                      "Delta~Electoral~democracy",
                      "Electoral~democracy[t-1]",
                      "Delta~Minoritarian~democracy",
                      "Minoritarian~democracy[t-1]",
                      "Delta~Log~GDP",
                      "Log~GDP[t-1]",
                      "Delta~Corruption",
                      "Corruption[t-1]")),
                levels = rev(c("Support[t-1]",
                               "Support[t-2]",
                               "Delta~Electoral~democracy",
                               "Electoral~democracy[t-1]",
                               "Delta~Minoritarian~democracy",
                               "Minoritarian~democracy[t-1]",
                               "Delta~Log~GDP",
                               "Log~GDP[t-1]",
                               "Delta~Corruption",
                               "Corruption[t-1]")))

plot_RegAPSR2 <- dwplot(result_RegAPSR2, dodge_size = 0.8, by_2sd = FALSE) +
  scale_y_discrete(labels = parse(text = levels(terms4))) +
  scale_color_grey(start = 0.4, end = 0.8, guide = guide_legend(reverse = TRUE)) +
  # scale_color_uiowa(name = "", palette = "digitMixed") +
  labs(
    title = "",
    subtitle = "Regime Specified w. Corruption"
  ) +
  facet_wrap(~type, scales = "free_x") +
  theme(legend.position = "bottom", 
        legend.title = element_blank())

grid.arrange(plot_APSR1, plot_APSR2, plot_RegAPSR1, plot_RegAPSR2, legend, ncol = 1)
```

@@

>>>>

@@

>>>>>>> 7257990cf1c7c4951fc068aacaa22c22bc503a86
